---
title: "Human Activity Recognition Project"
author: "Barbier de Reuille, Pierre"
date: "17/12/2014"
output: html_document
---

Introduction
============

In this project, we are going to analyse data about weight lifted exercises coming from http://groupware.les.inf.puc-rio.br/har.
In this experiment, the team asked a number of non-experienced weight lifters to exercise either correctly or incorrectly,
but with a specific error. The exercise was supervied by an experienced trainer to ensure it was performed either correctly
or with the right error.

The data is loaded like this:

```{r}
# Libraries needed for the whole study
library(ggplot2)
library(caret)
library(dplyr)
library(randomForest)

data <- tbl_df(read.csv("pml-training.csv"))
```

Cleaning the data
=================

First, the data contained some division by zero errors. These have been replaced by simple NA using a standard text editor.

In the datasets, many variables


```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
